Experience Report: Distributed Computing for the Common Man

### 2010-03-22 doc/icfp-2010/main.tex
just started correcting/modifying sec.4.2.3 [KK]

As explained in Section~\ref{sec:API}, the \of{Network} module is
actually providing three different implementations, according to three
different execution scenarios (namely, \of{Same}, \of{Poly} and
\of{Mono}). There is actually a single, generic implementation, which
is then instantiated in three different ways.
The generic implementation assumes that we are only transmitting
strings over the network, as evident from \of{Assign} and
\of{Completed} messages in the protocol section~\ref{sec:protocol}.
Therefore, the signature for the generic implementation is as follows:
\begin{ocaml}
  generic_master:
    assign_job:('a -> string * string) ->
    master:('a * 'c -> string -> ('a * 'c) list)  ->
    ('a * 'c) list -> unit
\end{ocaml}
The first argument \of{assign_job} is a function indicating 
the two strings to pass inside the \of{Assign} message of the protocol.
We can now distinguish the three cases:
\begin{description}
\item[\of{Same}:] in this case, \of{assign_job} is simply returning
  the marshaled closure together with the marshaled value.
\item[\of{Poly}:] in this case, \of{assign_job} is simply
  returning the marshaled value (the first string being meaningless in
  this context).
\item[\of{Mono}:] in this case, \of{assign_job} is immediately
  returning its argument (the first string being meaningless in
  this context).
\end{description}

>>>>

As mentioned in Section~\ref{sec:API}, the \of{Network} module is
actually providing three different implementations, according to three
different execution scenarios (namely, \of{Same}, \of{Poly} and
\of{Mono}). The exciting thing about our library is that there is
actually a single, generic implementation, which is then instantiated
in three different ways, corresponding to the three scenarios.  The
generic implementation assumes that only string are being transmitting
over the network, as evident from \of{Assign} and \of{Completed}
messages in Section~\ref{sec:protocol}.  The signature for the generic
implementation is therefore as follows:
\begin{ocaml}
  generic_master:
    assign_job:('a -> string * string) ->
    master:('a * 'c -> string -> ('a * 'c) list)  ->
    ('a * 'c) list -> unit
\end{ocaml}
The first argument \of{assign_job} is a function indicating 
the two strings to pass inside the \of{Assign} message of the protocol.
We can now distinguish the three cases:
\begin{description}
\item[\of{Same}:] in this case, \of{assign_job} is simply returning
  the marshaled closure together with the marshaled value.
\item[\of{Poly}:] in this case, \of{assign_job} is simply
  returning the marshaled value (the first string being meaningless in
  this context).
\item[\of{Mono}:] in this case, \of{assign_job} is immediately
  returning its argument (the first string being meaningless in
  this context).
\end{description}
